### 2015-07-05 narrative/enabling_tech.tex
fixed typo and clarifying enabling tech`

The Sirocco API is much more complex than a standard POSIX call prompting
layering a more user friendly interface on top. The ADIOS~\cite{adios} API
offers an API nearly as simple as POSIX, but with the ability to change the
actual data transport mechanism without changing the source code. This affords
writing to a single output API while shifting from writing to a POSIX file
system, some middleware like DataSpaces~\cite{dataspaces}, or some other system
like Sirocco all without changing the source code. ADIOS has proven effective
for writing to POSIX file systems, data staging
systems~\cite{predata,dataspaces,nessie}, workflow systems~\cite{flexpath}, and
even nothing through the use of a NULL transport.

>>>>

The LWFS philosophy focuses on providing a universal core with additional
semantics and services layered on top or run along side. For this project, the
Sirocco API is much more complex than a standard POSIX call prompting layering
a more user friendly interface on top. Placing a thin, optimized layer as part
of the storage system will offer the kinds of functionality and semantics this
project proposes. From the user perspective, something like the
ADIOS~\cite{adios} API offers an API nearly as simple as POSIX, but with the
ability to change the actual data transport mechanism without changing the
source code. This affords writing to a single output API while shifting from
writing to a POSIX file system, some middleware like
DataSpaces~\cite{dataspaces}, or some other system like Sirocco all without
changing the source code. ADIOS has proven effective for writing to POSIX file
systems, data staging systems~\cite{predata,dataspaces,nessie}, workflow
systems~\cite{flexpath}, and even nothing through the use of a NULL transport.
Part of this project's goals seeks to understand where the dividing line
between the storage layer shared by all users and middleware being used by a
single or small number of users.

### 2015-07-05 narrative/intro.tex
editing of intro
fixed typo and clarifying enabling tech`

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time knowledge" from 
scientific computing, aligns perfectly with this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

@@

However, the most significant problem occurs after the simulation run completes. Basic visualizations from the reducted data, just to get a high-level view of the simulation, can take significant time. While some timesteps might be on disk, others are archived on tape (where transfer could take weeks). Further, visualization of detailed views of the simulation are even more complicated.

>>>>

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time knowledge'' from 
scientific computing, aligns perfectly with this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

@@

However, the most significant problem occurs after the simulation run completes. Basic visualizations from the reducted data, just to get a high-level view of the simulation, can take significant time. While some timesteps might be on disk, others are archived on tape (where transfer could take weeks). Further, visualization and analysis of detailed views of the simulation are even more complicated.
